---
title: "Wen Zhang Q2"
author: "Wen Zhang"
date: "2019Äê8ÔÂ22ÈÕ"
output: html_document
---

### Q2
#### part(a)
The amount of Scott's loan, interest rate and term are the same as that of Bill's in question 1.Regardless of interest offset account, Scott need to pay the same amount of annual repayment as Bill.

```{r}
i=.035; n=30; v=1/(1+i)
f1<-function(x) {600000-x*(1-(1/(1+i))^n)/i}
x <- uniroot(f1,c(30000,40000), tol=0.0001)
x$root
```

#### part(b)

The real annual repayment is equal to repayment in part (a) plus the interests from interest offset account. At the end of term, $100000 in the interest offset account offsets the amount owe on loan. Discounting the annual repayment and 100000 paid at the end of n years to the start of the term, the amount need to be equal to the amount of loan.
Using uniroot function, n = 22.35. Because the term needs to be an integer, it is a 23-year-term loan.

The real final repayment is equal to the amount of loan minus the present value of real anuual repayment during 22-year-term. Accummulating the real final repayment to the end of 23th year, last payment is accummulated amount minus $100000, then minus the interests from interest offset account.

```{r}
f2<-function(n) {600000-(x$root+100000*i)*(1-(1/(1+i))^n)/i-100000*v^n}
n<- uniroot(f2,c(20,30),tol = 0.0001)
n$root

lastpayment=(600000-(x$root+100000*i)*(1-(1/(1+i))^22)/i)*(1+i)^23-100000*i-100000
lastpayment
```