---
title: "Untitled"
author: "Wen Zhang"
date: "2019Äê8ÔÂ22ÈÕ"
output: html_document
---

### Q4

```{r}
library("timevis")
library("lubridate")
date1 <- c("1994-06-22", "1993-07-21","1996-04-29")
deathdate <- as.Date(date1)
deathdate. <- as.Date(date1)
date2<-c("1965-05-16","1922-03-01","1942-09-21")
birthdate<-as.Date(date2)
birthdate.<-as.Date(date2)
```

#### part(a)
Calculating the number of years between the date of birth and date of death then rounding the number to largest integers not greater than it. The number is the age when life was dead. The number plus 1 is the age next birthday at death.
```{r}
floor(time_length(difftime(deathdate,birthdate),"years"))+1 
```

#### part(b)
Changing the deathdate to the 1 January of the death year and calculating the number of years between 1 January of the death year to the date of birth. Rounding the number to largest integers not greater than it. The number is the age when life was dead is the age last birthday.
```{r}
month(deathdate.)<-1;day(deathdate.)<-1
floor(time_length(difftime(deathdate.,birthdate.),"years"))
```

#### part(c)
Because the dates of birth were early than the dates of death in the policy year of death in life A, B and C.Therefore, the rounding number of years between the date of birth and date of death is age at the birthday in the policy year of death.
floor(time_length(difftime(deathdate,birthdate),"years"))








